Covariate Analysis of MAYO Reprocessed counts Regressing out Diagnosis as well for TWAS

### 2020-05-23 code/prepscripts/Mayo_TranscriptNorm.Rmd
Trans DE MSBB

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (CBE, TCX)';
CODE <- syn_temp$store(synapseclient$Folder(name = "Mayo", parentId = parentId))
#Set Used SynIDs For Provenance
Syns_Used <- c( "syn10499227","syn10507722","syn3817650","syn5223705","syn8698214","syn8698211","syn22087693","syn6126119","syn6126114","syn20801992")

>>>>

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with CQN normalisation (CBE, TCX)';
CODE <- syn_temp$store(synapseclient$Folder(name = "Mayo", parentId = parentId))
#Set Used SynIDs For Provenance
Syns_Used <- c( "syn10499227","syn10507722","syn3817650","syn5223705","syn8698214","syn8698211","syn22087693","syn6126119","syn6126114","syn20801992")
